--- 
title: |
  | Introduction to Machine Learning
  | (NPFL054)
author: "François Leroy, PhD student at CZU"
date: "`r Sys.Date()`"
output: pdf_document
documentclass: report
classoption: oneside
fontsize: 12pt
linestretch: 1.5
geometry:
- left = 2cm
- right = 2cm
- top = 2cm
- bottom = 2cm
colorlinks: yes
link-citations: yes
github-repo: FrsLry/HW1_ML_CUNI_leroy
subtitle: Homework 2
---

```{r, echo = F}
knitr::opts_chunk$set(warning = F,
                      message = F)
```

# Set up the project {-}

```{r}
library(ISLR) # for the data
library(tidyverse) # convenient
library(rpart) # for decision trees
library(randomForest) # for ensemble learning
library(glmnet) # for regularized logistic regression
library(ROCR) # for ROC curves
```

```{r}
## Reproduce the result
set.seed(123)
## Create the splitting vector
split <- sample(nrow(Caravan), 1000)
## Create the test dataset
d_test <- Caravan[split,]
## Create the training dataset
d_train <- Caravan[-split,]
```


# Task 1 - Data analysis

* **First, check the distribution of the target attribute. What would be your precision if you select 100 examples by chance?**

```{r}
round(table(Caravan$Purchase), 2)
```

```{r, echo=F}
Caravan %>% 
  ggplot()+
  geom_bar(aes(x = Purchase, y = ..prop.., group = 1), stat = "count")+
  ylab("Proportion")+
  theme_bw()
```

We can see that there is `r paste0(round(table(Caravan$Purchase)/nrow(Caravan), 2)[1]*100, "%")` of customers who didn't purchase  the insurance and that `r paste0(round(table(Caravan$Purchase)/nrow(Caravan), 2)[2]*100, "%")` who did. As the precision is the number of examples classified as *Yes* when the value is actually *Yes*, by chance, the precision should be `r round(table(Caravan$Purchase)/nrow(Caravan), 2)[2]`.

* **1.a. Focus on the customer type MOSHOOFD: create a table with the number of customers that belong to each of 10 L2 groups and the percentage of customers that purchased a caravan insurance policy in each group. Comment the figures in the table. Then do the same for the customer subtype MOSTYPE (41 subgroups defined in L1).** 

\underline{MOSHOOFD type:}

```{r}
Caravan %>% 
  count(MOSHOOFD, Purchase) %>% 
  group_by(MOSHOOFD) %>% 
  summarise(size = sum(n),
            purchase_prop = round(n[Purchase == "Yes"]/sum(n), 2)) %>% 
  rename(group = MOSHOOFD) %>% 
  kableExtra::kable()
```

From this first table, we can see that the customers that are more prone to purchase an insurance (13% of them) are the one belonging to the group 2, *i.e.* the *driven growers*. On the other hand, the customers belonging to the class 6 and 10, respectively the *cruising seniors* and the *farmers*, are less likely to subscribe to the insurance (only 2% in each group).

\underline{MOSHOOFD type:}

```{r}
table <- 
Caravan %>% 
  count(MOSTYPE, Purchase) %>% 
  group_by(MOSTYPE) %>% 
  summarise(size = sum(n),
            purchase_prop = round(n[Purchase == "Yes"]/sum(n), 2)) %>% 
  rename(group = MOSTYPE) %>% 
  arrange(desc(purchase_prop))
## Display in 2 columns
kableExtra::kable(list(table[1:(nrow(table)/2),], 
                       table[((nrow(table)/2)+1):nrow(table),])) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

The two groups more prone to buy an insurance are the group 8 and 12, which correspond respectively to *middle class families* and *affluent young families*. Thus, we can say that families are potential good targets to sell insurances. We can see that the class 25, 26, 27 and 29 all have a low proportion of individuals buying a insurance. They are all related to old people (*i.e.*, *Young seniors in the city*, *Own home elderly*, *Seniors in apartments*, *Porchless seniors: no front yard*). Thus, old people are not a good target to sell insurances. 

**1.b. Analyze the relationship between features MOSHOOFD and MOSTYPE.**

```{r}
Caravan %>% 
  ggplot(aes(y = MOSTYPE, x = MOSHOOFD))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_bw()
```

We can clearly see a relationship between these two features which are MOSHOOFD = *Customer main type* and MOSTYPE = *Customer Subtype*. This is expected because MOSTYPE is just a more precise social position. For instance, we can see that when $MOSHOOFD = 10$, $MOSTYPE = 40 | 41$. We can see that $MOSHOOFD = 10$ correspond to *Farmers* and that $MOSTYPE = 40 | 41$ are two subclasses of farmers: *Large family farms* and *Mixed rurals*, respectively. 

# Task 2 - Model fitting, optimization, and selection
